---
title: "Lewisham Cycle Parking Targets"
author: "Jorge Martínez López (for Lewisham Cyclists)"
license: GPLv3
output: 
  html_document:
    theme: cosmo
    toc: false
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("dplyr")
library("osmdata")
library("htmltools")
library("sf")
library("leaflet")
library("leaflet.extras")
```

```{r, functions, echo=FALSE, message=FALSE, warning=FALSE}

boundary_box <-
  getbb ('London Borough of Lewisham', format_out = 'polygon')

makePopup <- function(points, osm_type) {
  points <- points %>%
    dplyr::mutate(
      popup = paste0(
        "<b>Cycle Parking</b><br/>",
        "Type: ",
        htmlEscape(points$bicycle_parking),
        "<br/>",
        "Capacity: ",
        htmlEscape(points$capacity),
        "<br/>",
        "Covered: ",
        htmlEscape(points$covered),
        "<br/>",
        "Access: ",
        htmlEscape(points$access),
        "<br/>",
        "Description: ",
        htmlEscape(points$description),
        "<br/>",
        "<a href=\"https://www.openstreetmap.org/",
        osm_type,
        "/",
        htmlEscape(points$osm_id),
        "\"><b>View</b> in map</a>",
        "<br/>",
        "<a href=\"https://www.openstreetmap.org/edit?",
        osm_type,
        "=",
        htmlEscape(points$osm_id),
        "\"><b>Edit</b> in OpenStreetMap</a>"
      )
    )
  return(points)
}

getPointMap <- function(parkingPoints) {
  icons <- awesomeIcons(
    icon = "bicycle",
    iconColor = "lightgray",
    library = "fa",
    markerColor = "red",
    spin = FALSE,
    extraClasses = NULL,
    squareMarker = FALSE,
    iconRotate = 0,
    fontFamily = "sans",
  )
  
  map <- parkingPoints %>%
    leaflet(height = "800px", width = "100%") %>%
    setView(lat = 51.4536,
            lng = -0.0180,
            zoom = 13) %>%
    addProviderTiles(providers$CartoDB.Positron) %>%
    addAwesomeMarkers(icon = icons,
                      popup = parkingPoints$popup,) %>%
    leaflet.extras::addResetMapButton() %>%
    leaflet.extras::addControlGPS(
      options = gpsOptions(
        position = "topright",
        activate = FALSE,
        autoCenter = TRUE,
        maxZoom = NULL,
        setView = TRUE
      )
    )
  return(map)
}

parking <- opq(bbox = boundary_box) %>%
  add_osm_feature(key = 'amenity', value = 'bicycle_parking') %>%
  add_osm_feature (key = "access", value = "!private") %>%
  osmdata_sf () %>%
  trim_osmdata (boundary_box) %>%
  unique_osmdata()

```

## Introduction

This page contains a few maps showing cycle parkings in Lewisham with missing or incorrect information.

For guidance on how to provide and edit cycle parking information please visit:

* <https://wiki.openstreetmap.org/wiki/Tag:amenity%3Dbicycle_parking>
* <https://wiki.openstreetmap.org/wiki/Key:bicycle_parking>

This map updates every night, your edits in OpenStreetMap won't be instantly reflected here.

## The maps {.tabset .tabset-fade .tabset-pills}

### Capacity

These cycle parking points do not have capacity information.
You can also add information about cargo bike parking.

Edit them on Open Street Map and add the tag "capacity".

More information:

* <https://wiki.openstreetmap.org/wiki/Key:capacity>
* <https://wiki.openstreetmap.org/wiki/Key:cargo_bike>

```{r echo=FALSE, capacity, warning=FALSE}

parking$osm_points [which (is.na(parking$osm_points$capacity)), ] %>%
  makePopup(osm_type="node") %>%
  getPointMap()

```

### Cover

These cycle parking points do not have cover information (protection from rain).

Edit them on Open Street Map and add the tag "covered".

More information:

* <https://wiki.openstreetmap.org/wiki/Key:covered>

```{r echo=FALSE, covered, warning=FALSE}

parking$osm_points [which (is.na(parking$osm_points$covered)), ] %>%
  makePopup(osm_type="node") %>%
  getPointMap()

```

### Access

These cycle parking points do not have access information (public, customers, etc).

Edit them on Open Street Map and add the tag "access".

More information:

* <https://wiki.openstreetmap.org/wiki/Key:access>

```{r echo=FALSE, access, warning=FALSE}

parking$osm_points [which (is.na(parking$osm_points$access)), ] %>%
  makePopup(osm_type="node") %>%
  getPointMap()

```

### Polygons

These cycle parking spots are included in the map as polygons. While this is allowed, it might not be consistent if the parking is a group of stands or a small shed as opposed to a building or a cycle hub.

Please consider removing the polygon and using points instead.

More information:

* <https://wiki.openstreetmap.org/wiki/Tag:amenity%3Dbicycle_parking>

```{r echo=FALSE, polygon, warning=FALSE}

parking$osm_polygons %>%
  st_transform(crs = 32632) %>%
  st_centroid() %>%
  st_transform(crs = 4326) %>%
  makePopup(osm_type="way") %>%
  getPointMap()

```
